### 2015-07-19 implementation-environment.tex
Tighten.

Spack's compiler wrappers have a number of useful effects.  First, they allow
Spack to transparently switch compilers in most builds.  This is how
compiler options like {\tt \%gcc} are implemented.  Second, they enforce the
use of {\tt RPATHs} in
installed binaries.  This causes applications built by Spack to run correctly
{\it regardless of the environment}.  Third, because compiler wrappers add 
header and library search paths for dependencies, header and library detection
tests that are run by most build systems succeed automatically, without
the need to use special arguments for nonstandard locations.  {\tt configure}
commands in Spack's {\tt install} function can have fewer arguments, and can
be written as they would be for system installs.  This reduces complexity
for package maintainers and helps to ensure consistent, reproducible
build policies across packages.  Finally, because Spack has control over the 
wrappers, package authors can programmatically filter the compiler flags
used by software build systems, a useful last resort when porting to
bleeding-edge platforms or new, esoteric compilers.

>>>>

Spack's compiler wrappers have a number of benefits.  First, they allow
Spack to transparently switch compilers in most builds.  This is how
compiler options like {\tt \%gcc} are implemented.  Second, they enforce the
use of {\tt RPATHs} in
installed binaries.  This causes applications built by Spack to run correctly
{\it regardless of the environment}.  Third, because compiler wrappers add 
header and library search paths for dependencies, header and library detection
tests used by most build systems succeed automatically, without
the need to use special arguments for nonstandard locations.  {\tt configure}
commands in Spack's {\tt install} function can have fewer arguments, and can
be written as they would be for system installs.  This reduces complexity
for package maintainers and helps to ensure consistent, reproducible
build policies across packages.  Finally, because Spack has control over the 
wrappers, package authors can programmatically filter the compiler flags
used by software build systems, a useful last resort when porting to
bleeding-edge platforms or new, esoteric compilers.
